Naturalness in U(1) extensions of the MSSM

### 2015-01-15 paper/e6ssm-tuning-paper.tex
Added a note explaining notation I am using to try to shorten the expressions for the RGEs, when the numerical values of the U(1)' charges are not substituted in. The length of the general USSM 2-loop RGEs may still be an issue, though.
Adding in the 2-loop betas, however the sums over charges (unless I am missing something) don't at this stage match the special case of the cE6SSM - something to check?
Rewrote a coefficient in beta function for \lambda in more compact notation
Wrote coefficient of g_1'^4 in 2-loop beta function for \lambda more compactly
maded MSSM stop and higgs plots part of

\section{\label{sec:results}Results}
% Our results. Plots to go in here:
%    - tuning as a function of stop mass for the MSSM and E6SSM
As discussed in the introduction many recent papers have focussed on
light stops as allowing natural SUSY and there has been a lot of
theoretical effort to find SUSY models with a $125$ GeV Higgs boson
while still having light stops and experimental efforts to search for
light stops.  This is entirely appropriate since there are many good
reasons to expect the soft masses to be set at high energies.  However
that is not the only possibility and the fine tuning problem depends
strongly the RG evolution from the GUT scale, as the soft Higgs masses
that appear in the EWSB conditions pick up contributions from the soft
squark masses.

\begin{figure}[h]
\begin{center}
\resizebox{!}{10cm}{%
\includegraphics{mssm_stop_tuning.png}}
\caption{Scatter plot of fine tuning in the MSSM as a function of
the lightest stop mass, $m_{\tilde{t}_1}$, for the cut-off scales (from 
bottom to top) $M_X=20$ TeV, $M_X=50$ TeV, $M_X=100$ TeV and $M_X=10^{16}$ GeV.}
\label{Fig:mssmstoptuning}
\end{center}
\end{figure}

% DH:: I'm not sure if this is worth including? I've put a disclaimer in the
% text, as well.
\begin{figure}[h]
\begin{center}
\resizebox{!}{10cm}{%
\includegraphics{mssm_higgs_tuning.png}}
\caption{Scatter plot of fine tuning in the MSSM as a function of
the lightest Higgs mass, $m_{h_1}$, for the cut-off scales (from 
bottom to top) $M_X=20$ TeV, $M_X=50$ TeV, $M_X=100$ TeV and $M_X=10^{16}$ GeV.}
\label{Fig:mssmhiggstuning}
\end{center}
\end{figure}
To illustrate this, in Fig.~\ref{Fig:mssmstoptuning} we show the
variation in fine tuning when we scan over the stop masses and mixing,
with $500 \textrm{ GeV} \leq m_{Q_3},m_{u_3}\leq 10\textrm{ TeV}$ and
$-3810\textrm{ GeV}\leq A_t\leq -20\textrm{ GeV}$, for $M_X=20$ TeV,
$50$ TeV and $100$ TeV.  The remaining parameters we fix such that at
$M_{SUSY}$ they have the values $\mu=-97.5$ GeV, $B=-84.8$ GeV,
$M_1=92.1$ GeV, $M_2=95.9$ GeV, $M_3=352$ GeV, $A_b=-117.9$ GeV,
$A_\tau=-7.8$ GeV, $m_{L_i}=400$ GeV, $m_{e_i}=204$ GeV,
$m_{Q_{1,2}}=438$ GeV, $m_{u_{1,2}}436$ GeV and $m_{d_i}=438$ GeV
($i=1,2,3$). Although we should stress that making this choice will
lead to a spectrum which is in conflict with the LHC limits, doing so
ensures that fine tuning due to the other parameters is small, so that
we avoid washing out the fine tuning impact of the stops when the
tuning is small\footnote{For models in which the spectrum is heavier,
  when the stop masses are small the fine tuning reaches a lower bound
  imposed by other heavier parameters.} as can be the case when the
stop masses are less than 1 TeV.  Note that the Higgs mass is also
allowed to vary in this scan, as shown in
Fig.~\ref{Fig:mssmhiggstuning}. This reveals the tuning problem which
people have been worrying about since the discovery of the 125 GeV
Higgs boson as we see that raising the stop masses is also pushing up
the Higgs mass, meaning that heavier Higgs masses require more fine
tuning.  However for a low value of the UV scale this tuning is not so
severe unless the stops are very heavy, and a 125 geV Higgs can be
obtained without much tuning in this unrealistic case where we have
minimised other sources of tuning.  On the other hand the tuning
becomes more severe as we increase the cutoff such that for $M_X =
10^{16}$ GeV a lightest stop masses of $1-3$ TeV can result in a fine
tuning of $\approx 200 - 1000$ as shown in
Fig.~\ref{Fig:mssmstoptuning} and the minimum tuning we see consistent
with a $125$ GeV Higgs is $\approx 200$, as shown in
Fig.~\ref{Fig:mssmhiggstuning}.

@@

As is shown in Fig.~\ref{} the tuning in the MSSM becomes larger
than that of the E$_6$SSM when the cutoff scale is ?

@@

\beta_\lambda^{(2)}&=\lambda \left [ \left ( \right )g_1'^4\right ],\label{eq:USSMLambdaBetaTwoLoop}

@@

>>>>

\section{\label{sec:results}Results}
% Our results. Plots to go in here:
%    - tuning as a function of stop mass for the MSSM and E6SSM
As discussed in the introduction many recent papers interested in
natural supersymmetry have focussed on light stops, with much
theoretical effort to find models where it is easier to get a $125$
GeV Higgs boson and light stops simultaneously and much experimental
efforts to search for light stops.  This is entirely appropriate since
there are many good reasons to expect the soft masses to be set at
high energies.  However that is not the only possibility and the fine
tuning problem depends strongly on the RG evolution from the GUT
scale, as the soft Higgs masses that appear in the EWSB conditions
pick up contributions from the soft squark masses.

\begin{figure}[h]
\begin{center}
\resizebox{!}{6cm}{%
\includegraphics{mssm_stop_tuning.png}}
\resizebox{!}{6cm}{%
\includegraphics{mssm_higgs_tuning.png}}
\caption{Left panel: Scatter plot of fine tuning in the MSSM as a function of
the lightest stop mass, $m_{\tilde{t}_1}$, for the cut-off scales (from 
bottom to top) $M_X=20$ TeV, $M_X=50$ TeV, $M_X=100$ TeV and $M_X=10^{16}$ GeV. 
Right panel: Scatter plot of fine tuning in the MSSM as a function of
the lightest Higgs mass, $m_{h_1}$, for the cut-off scales (from 
bottom to top) $M_X=20$ TeV, $M_X=50$ TeV, $M_X=100$ TeV and $M_X=10^{16}$ GeV.}
\label{Fig:mssmstoptuning}
\end{center}
\end{figure}
To illustrate this, in the left panel of Fig.~\ref{Fig:mssmstoptuning}
we show the variation in fine tuning when we scan over the stop masses
and mixing, with $500 \textrm{ GeV} \leq m_{Q_3},m_{u_3}\leq
10\textrm{ TeV}$ and $-3810\textrm{ GeV}\leq A_t\leq -20\textrm{
  GeV}$, for $M_X=20$ TeV, $50$ TeV and $100$ TeV.  The remaining
parameters we fix such that at $M_{SUSY}$ they have the values
$\mu=-97.5$ GeV, $B=-84.8$ GeV, $M_1=92.1$ GeV, $M_2=95.9$ GeV,
$M_3=352$ GeV, $A_b=-117.9$ GeV, $A_\tau=-7.8$ GeV, $m_{L_i}=400$ GeV,
$m_{e_i}=204$ GeV, $m_{Q_{1,2}}=438$ GeV, $m_{u_{1,2}}436$ GeV and
$m_{d_i}=438$ GeV ($i=1,2,3$). Although we should stress that making
this choice will lead to a spectrum which is in conflict with the LHC
limits, doing so ensures that fine tuning due to the other parameters
is small, so that we avoid washing out the fine tuning impact of the
stops when the tuning is small\footnote{For models in which the
  spectrum is heavier, when the stop masses are small the fine tuning
  reaches a lower bound imposed by other heavier parameters.} as can
be the case when the stop masses are less than 1 TeV.  Note that the
Higgs mass is also allowed to vary in this scan, as shown in the right
panel of Fig.~\ref{Fig:mssmstoptuning}. This illustrates the tuning
problem which people have been worrying about since the discovery of
the 125 GeV Higgs boson as we see that raising the stop masses is also
pushing up the Higgs mass, meaning that heavier Higgs masses require
more fine tuning.  However for a low value of the UV scale this tuning
is not so severe unless the stops are very heavy, and a 125 geV Higgs
can be obtained without much tuning in this unrealistic case where we
have minimised other sources of tuning.  On the other hand the tuning
becomes more severe as we increase the cutoff such that for $M_X =
10^{16}$ GeV a lightest stop masses of $1-3$ TeV can result in a fine
tuning of $\approx 100 - 1000$ and the minimum tuning we see consistent
with a $125$ GeV Higgs is $\approx 200$, as shown in
Fig.~\ref{Fig:mssmstoptuning}.

@@

To examine this further we also looked at how the tuning compares between the MSSM and E6SSM As is shown in Fig.~\ref{} the tuning in the MSSM becomes larger
than that of the E$_6$SSM when the cutoff scale is ?

@@

\beta_\lambda^{(2)}&=\lambda \bigg \{ -2\lambda^2\left ( \lambda^2+2\Sigma_\lambda+3\Sigma_\kappa\right )-4\Pi_\lambda-6\Pi_\kappa-3\lambda^2\left ( 3y_t^2+3y_b^2+y_\tau^2\right ) \nonumber\\
&{} -3\left ( 3y_t^4+3y_b^4+2y_t^2y_b^2+y_\tau^2 \right )+6g_2^2\Sigma_\lambda+g_1^2\left ( \frac{4}{5}y_t^2-\frac{2}{5}y_b^2+\frac{6}{5}y_\tau^2+\frac{4}{5}\Sigma_\kappa +\frac{6}{5}\Sigma_\lambda\right )\nonumber\\
&{}\left.+g_1'^2\left [ 4\tilde{Q}_S^2\lambda^2 -6\left ( \tilde{Q}_2^2-\tilde{Q}_Q^2-\tilde{Q}_u^2\right )y_t^2-6\left ( \tilde{Q}_1^2-\tilde{Q}_Q^2-\tilde{Q}_d^2\right )y_b^2 \right.\right.\nonumber\\
&{}\left.-2\left ( \tilde{Q}_1^2-\tilde{Q}_L^2-\tilde{Q}_e^2\right )y_\tau^2-6\left ( \tilde{Q}_S^2-\tilde{Q}_D^2-\tilde{Q}_{\overline{D}}^2 \right )\Sigma_\kappa-4\left ( \tilde{Q}_S^2-\tilde{Q}_1^2-\tilde{Q}_2^2\right )\Sigma_\lambda\right ]\nonumber\\
&{}+16g_3^2\left ( y_t^2+y_b^2+\Sigma_\kappa\right ) +\frac{33}{2}g_2^4+\frac{297}{50}g_1^4+2g_1'^4\left [ 2\tilde{Q}_1^4+2\tilde{Q}_2^4+2\tilde{Q}_S^4+\left ( \tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2\right )\Sigma_{\tilde{Q}}\right ]\nonumber\\
&{}+\frac{9}{5}g_1^2g_2^2+6g_1'^2g_2^2\left ( \tilde{Q}_1^2+\tilde{Q}_2^2\right )+\frac{6}{5}g_1^2g_1'^2\left [\tilde{Q}_1^2+\tilde{Q}_2^2+\left ( \tilde{Q}_2-\tilde{Q}_1\right )\Sigma_{\tilde{Q}}^Y\right ]\bigg \},\label{eq:USSMLambdaBetaTwoLoop}

@@

Additionally, in order to keep our expressions compact we also use the notation
\Sigma_{\tilde{Q}}=\sum_i \tilde{Q}_i^2, \qquad \Pi_{\tilde{Q}}=\sum_i \tilde{Q}_i^4
to denote sums over the $U(1)'$ charges, and
\Sigma_{\tilde{Q}}^Y&=\sum_i \sqrt{\frac{5}{3}}Q_i^Y\tilde{Q}_i\\
&=-3\tilde{Q}_1+3\tilde{Q}_2+3\tilde{Q}_d-3\tilde{Q}_D+3\tilde{Q}_e-3\tilde{Q}_L+3\tilde{Q}_Q-6\tilde{Q}_u+3\tilde{Q}_{\overline{D}}+\tilde{Q}_{\overline{H'}}-\tilde{Q}_{H'}.
Note that in these expressions the $U(1)_Y$ and $U(1)'$ charges are assumed to be GUT-normalised.
